Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-09 report/report.tex
Update todo
Increase TOC depth and add subsections to Delimitations section

\setlength\parindent{0pt}
\setlength{\parskip}{1em}
\setcounter{tocdepth}{1}

@@

\begin{enumerate}
    \item The primary subquestion is: \textbf{How many roads of each type will collide with some other map feature, once they have been given a geometrical width?}. This question aims to find the rate of collision between road features in OSM, and investigate the nature of the most common types of collisions and how they can be corrected.
    \item The secondary subquestion is: \textbf{What is the positional accuracy of OSM map features compared to a reference map?}. The positional accuracy will be neccessary to carry out the investigation of the first subquestion: the rate of collisions between roads, since it will determine the maximum tolerance in distance between road points before a collision is certain to have occured.
\end{enumerate}

@@

@@

@@

% TODO: Read over the sample report to see what they have in the background section

>>>>

\setlength\parindent{0pt}
\setlength{\parskip}{1em}
\setcounter{tocdepth}{2}

@@

\begin{enumerate}
    \item The primary subquestion is: \textbf{How many roads of each type will collide with some other map feature, once they have been given a geometrical width?} This question aims to find the rate of collision between road features in OSM, and investigate the nature of the most common types of collisions and how they can be corrected.
    \item The secondary subquestion is: \textbf{What is the positional accuracy of OSM map features compared to a reference map?}. The positional accuracy will be neccessary to carry out the investigation of the first subquestion: the rate of collisions between roads, since it will determine the maximum tolerance in distance between road points before a collision is certain to have occured.
\end{enumerate}

@@

\subsection{Delimitations of the OSM map data}

@@

\subsection{Delimitations of accuracy classes}

@@

% TODO: Extend 2.3 with more content and references
